---
title: "Causality experiments"
output:
  pdf_document: default
  html_notebook: default
---


```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(ggthemes)
library(forcats)
library(knitr)
theme_set(theme_few())

data.path <- "../data/pilots/"

readData <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-trials.csv", sep = "")))
}

readSubjectInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-subject_information.csv", sep = "")))
}

readTurkInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-mturk.csv", sep = "")))
}
```


# To do

1. Get HIT completion time and remove Ps who complete task too quickly (clikc through)

### Overview of Experiments:


1. Causality 1 (5/8/2017): SWBD
2. Causality 2 (5/23/2017): WSJ w/ endorsement
3. Causality 2 SWBD (5/31/2017): SWBD w/ endorsement


### Subject information


Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-causality-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```



```{r}
df.cas <- readData("pilot-causality-1")  %>%
  mutate(verb.phrase = gsub("&quotechar", "", verb.phrase),
         entire.sentence = gsub("&quotechar", "", entire.sentence))
```

```{r}
df.cas.summary <- df.cas %>%
  group_by(entire.sentence, verb.phrase) %>%
  multi_boot_standard(column = "agreement")
```

```{r fig.width=10}
df.cas.summary <- df.cas.summary %>%
  ungroup() %>%
  mutate(entire.sentence = 
           factor(entire.sentence, levels = entire.sentence[order(mean)]))


ggplot(df.cas.summary, aes(x = entire.sentence, 
                           y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Causality judgment (1 = agree; 0 = disagree)")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```


Full distributions

By item

```{r fig.width=12}
df.cas %>%
  ggplot(., aes( x = agreement))+
  #geom_density()+
  geom_histogram()+
  facet_wrap(~entire.sentence)
```

By subject

```{r fig.width=12}
df.cas %>%
  ggplot(., aes( x = agreement))+
  geom_histogram()+
  facet_wrap(~workerid)
```


# Valence 2

### Subject information


Did people enjoy the experiment?

```{r}
df2.info <- readSubjectInfo("pilot-causality-2")
table(df2.info$enjoyment)
```
Comments?

```{r}
df2.info %>% select(comments) %>% filter(comments != "") %>% kable()
```



```{r}
df2.cas <- readData("pilot-causality-2")  %>%
  mutate(verb.phrase = gsub("&quotechar", "", verb.phrase),
         entire.sentence = gsub("&quotechar", "", entire.sentence))
```

### Table of items

```{r}
unique(df2.cas %>% select(tgrep.id, entire.sentence, verb.phrase)) %>%
  kable()
```



### Endorsements

```{r fig.width=10}
df.cas2.endorse.summary <- df2.cas %>%
  rowwise() %>%
  mutate(response = ifelse(choice == "Yes", 1, 0)) %>%
  group_by(entire.sentence, verb.phrase, tgrep.id) %>%
  multi_boot_standard(column = "response")

df.cas2.endorse.summary <- df.cas2.endorse.summary %>%
  ungroup() %>%
  mutate(tgrep.id = 
           factor(tgrep.id, levels = tgrep.id[order(mean)]))


# df.cas2.endorse.summary[with(df.cas2.endorse.summary, order(-mean)),] %>% kable()
ggplot(df.cas2.endorse.summary, aes(x = tgrep.id,
                           y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Endorsement")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```



```{r}
df.cas2.summary <- df2.cas %>%
  group_by(tgrep.id, entire.sentence, verb.phrase) %>%
  multi_boot_standard(column = "agreement")
```
### Causality judgments

```{r fig.width=10}
df.cas2.summary <- df.cas2.summary %>%
  ungroup() %>%
  mutate(tgrep.id = 
           factor(tgrep.id, levels = tgrep.id[order(mean)]))

ggplot(df.cas2.summary, aes(x = tgrep.id, 
                           y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Causality judgment (1 = agree; 0 = disagree)")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)

#df.cas2.summary[with(df.cas2.summary, order(-mean)),] %>% kable()
```

### Full distributions of causality judgments

```{r fig.width=8}
df2.cas %>%
  ggplot(., aes( x = agreement))+
  #geom_density()+
  geom_histogram()+
  facet_wrap(~tgrep.id)
```

By subject

```{r fig.width=8}
df2.cas %>%
  ggplot(., aes( x = agreement))+
  geom_histogram()+
  facet_wrap(~workerid)
```


### Endorsement vs. causality judgment

```{r}

left_join(
  df.cas2.endorse.summary %>%
    rename(endorse = mean, 
         endorse_lower = ci_lower,
         endorse_upper = ci_upper),
  df.cas2.summary %>%
  rename(causality = mean, 
         causality_lower = ci_lower,
         causality_upper = ci_upper)
) %>% ggplot(., aes (x = endorse, xmin = endorse_lower, xmax = endorse_upper,
                     y = causality, ymin = causality_lower,
                     ymax = causality_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  xlim(0.2, 1)+ylim(0.2,1)+ coord_fixed()+
  geom_abline(intercept = 0, slope = 1, lty = 3)

```

```{r}
df2.cas.byEndorse <- df2.cas %>%
  rowwise() %>%
  group_by(entire.sentence, verb.phrase, tgrep.id, choice) %>%
  multi_boot_standard(column = "agreement")


ggplot(df2.cas.byEndorse, aes( x = tgrep.id, y = mean, fill = choice, group = choice))+
  geom_col(position = position_dodge())+
  coord_flip()
```

Causality by endorsement (collapse item)

```{r}
df2.cas.byEndorse.collapseItem <- df2.cas %>%
  rowwise() %>%
  group_by(choice) %>%
  multi_boot_standard(column = "agreement")


ggplot(df2.cas.byEndorse.collapseItem, aes( x = choice, y = mean, fill = choice, group = choice, ymin = ci_lower,ymax = ci_upper))+
  geom_col(position = position_dodge())+geom_linerange()+
  coord_flip()
```

# Valence 2 SWBD

which includes endorsements

### Subject information

How long did it take people to complete the HIT?

```{r}
df2.sw.turk <-readTurkInfo("pilot-causality-swbd-2")
qplot(df2.sw.turk$Answer.time_in_minutes)
```



Did people enjoy the experiment?

```{r}
df2.sw.info <- readSubjectInfo("pilot-causality-swbd-2")
table(df2.sw.info$enjoyment)
```
Comments?

```{r}
df2.sw.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


Filter out people who finished the HIT in under 5 minutes...

```{r}
df2.sw.cas <- left_join(
  readData("pilot-causality-swbd-2")  %>%
  mutate(verb.phrase = gsub("&quotechar", "", verb.phrase),
         entire.sentence = gsub("&quotechar", "", entire.sentence)),
  df2.sw.turk %>% select(workerid, Answer.time_in_minutes) )%>% 
  filter(Answer.time_in_minutes > 5)
```

### Table of items

```{r}
unique(df2.sw.cas %>% select(tgrep.id, entire.sentence, verb.phrase)) %>%
  kable()
```



### Endorsements

```{r fig.width=10}
df.sw.cas2.endorse.summary <- df2.sw.cas %>%
  rowwise() %>%
  mutate(response = ifelse(choice == "Yes", 1, 0)) %>%
  group_by(entire.sentence, verb.phrase, tgrep.id) %>%
  multi_boot_standard(column = "response") %>%
  ungroup() %>%
  mutate(entire.sentence = 
           factor(entire.sentence, levels = entire.sentence[order(mean)]))


# df.cas2.endorse.summary[with(df.cas2.endorse.summary, order(-mean)),] %>% kable()
ggplot(df.sw.cas2.endorse.summary, aes(x = entire.sentence,
                           y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Endorsement")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```



### Causality judgments

```{r fig.width=10}
df2.sw.cas.summary <- df2.sw.cas %>%
  group_by(tgrep.id, entire.sentence, verb.phrase) %>%
  multi_boot_standard(column = "agreement") %>%
  ungroup() %>%
  mutate(entire.sentence = 
           factor(entire.sentence, levels = entire.sentence[order(mean)]))

ggplot(df2.sw.cas.summary, aes(x = entire.sentence, 
                           y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Causality judgment (1 = agree; 0 = disagree)")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)

#df.cas2.summary[with(df.cas2.summary, order(-mean)),] %>% kable()
```

### Full distributions of causality judgments

```{r fig.width=10}
df2.sw.cas %>%
  ggplot(., aes( x = agreement))+
  #geom_density()+
  geom_histogram()+
  facet_wrap(~entire.sentence)+
  xlab("causality judgment by item")
```

By subject

```{r fig.width=8}
df2.sw.cas %>%
  ggplot(., aes( x = agreement))+
  geom_histogram()+
  facet_wrap(~workerid)+
  xlab("causality judgment by worker")
```


### Endorsement vs. causality judgment

```{r}

left_join(
  df.sw.cas2.endorse.summary %>%
    rename(endorse = mean, 
         endorse_lower = ci_lower,
         endorse_upper = ci_upper),
  df2.sw.cas.summary %>%
  rename(causality = mean, 
         causality_lower = ci_lower,
         causality_upper = ci_upper)
) %>% ggplot(., aes (x = endorse, xmin = endorse_lower, xmax = endorse_upper,
                     y = causality, ymin = causality_lower,
                     ymax = causality_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.15)+
  geom_errorbarh(alpha = 0.15)+
  xlim(0, 1.01)+ylim(0,1.01)+ coord_fixed()+
  geom_abline(intercept = 0, slope = 1, lty = 3)

```

```{r fig.width =10}
df2.sw.cas.byEndorse <- df2.sw.cas %>%
  rowwise() %>%
  group_by(entire.sentence, verb.phrase, tgrep.id, choice) %>%
  multi_boot_standard(column = "agreement") %>%
  ungroup() %>%
  mutate(entire.sentence = 
           factor(entire.sentence, levels = entire.sentence[order(mean)]))


ggplot(df2.sw.cas.byEndorse, aes( x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper, fill = choice, group = choice))+
  geom_col(position = position_dodge())+ 
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("causality judgment by agreement")
```

Causality by endorsement (collapse item)

```{r}
df2.sw.cas.byEndorse.collapseItem <- df2.sw.cas %>%
  rowwise() %>%
  group_by(choice) %>%
  multi_boot_standard(column = "agreement")


ggplot(df2.sw.cas.byEndorse.collapseItem, aes( x = choice, y = mean, fill = choice, group = choice, ymin = ci_lower,ymax = ci_upper))+
  geom_col(position = position_dodge())+geom_linerange()+
  coord_flip()+
  ylab('causality judgment, collapse item')
```

