---
title: "Corpus generics modeling"
output: html_notebook
---


```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(ggthemes)
library(forcats)
library(knitr)
library(data.table)
theme_set(theme_few())

data.path <- "../data/pilots/"

readData <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-trials.csv", sep = "")))
}

readSubjectInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-subject_information.csv", sep = "")))
}
```


## Implied prevalence data

Run on 12/13/2017

```{r fig.width = 8, fig.height = 6}
df2.int <- readData("pilot-listener-prevalence-2")
# workerid1 had some problem
df2.int <- df2.int %>% filter(workerid != 1)

df2.int.summary <- df2.int %>%
  mutate(verb_phrase = gsub(",", "", verb_phrase),
         generic = paste(noun_phrase, verb_phrase, sep = " "),
         generic = gsub("&quotechar", "", generic)) %>%
  group_by(generic) %>%
  multi_boot_standard(col = "response")
```


Visualize implied prevalence data

```{r fig.width = 8}
df2.int.summary %>%
  ungroup() %>%
  mutate(generic = factor(generic, levels = generic[order(mean)])) %>% 
  ggplot(., aes(x = generic, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Implied prevalence")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```

## Endorsement data

Run on 12/27/2017

```{r fig.width = 8, fig.height = 6}
df.endorse <- readData("endorsement-1")

df.endorse.summary <- df.endorse %>%
  mutate(verb_phrase = gsub(",", "", verb_phrase),
         generic = paste(noun_phrase, verb_phrase, sep = " "),
         generic = gsub("&quotechar", "", generic),
         prevGroup = ifelse(prevalence < 20, 0.075,
                            ifelse(prevalence < 40, 0.275,
                                   ifelse(prevalence < 70, 0.575, -99)))) %>%
  group_by(generic, prevGroup) %>%
  multi_boot_standard(col = "response")
```


Load model results

```{r}
#m.0 <- fread("../models/results/results-corpgen-2betas-L0-smntcs_generic-25000_burn12500_lag20_chain1.csv")
#m.0 <- fread("../models/results/results-corpgen-n36-nullMixture-L0-smntcs_generic-50000_burn25000_lag20_chain1.csv")
#m.0 <- fread("../models/results/results-corpgen-n36-singleBetaPrior-L0-smntcs_generic-50000_burn25000_lag20_chain1.csv")
m.0 <- fread('../models/results/results-corpgen-singleBetaPrior-L0-S1partialData-smntcs_generic-10000_burn5000_lag20_chain1.csv')

```


Implied prevalence data

```{r}
m.pred <- m.0 %>% 
  filter(param == "generic") %>% rename(generic = category) %>%
  select(generic, val) %>%
  group_by(generic) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

md <- left_join(
  df2.int.summary, m.pred
  )


md <- md %>% mutate(sqErr = (MAP-mean)^2)

with(md, cor(MAP, mean))

ggplot(md, aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                 y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_point()+
  geom_errorbar(alpha = 0.3)+
  geom_errorbarh(alpha = 0.3)+
  coord_fixed()+
  xlim(0.15, 0.9)+
  ylim(0.15, 0.9)
```
Endorsement data
```{r}

m.pred.endorse <- m.0 %>% 
  filter(type == "endorsement") %>% 
  rename(generic = category, prevGroup = param) %>%
  select(generic, prevGroup, val) %>%
  group_by(generic, prevGroup) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val)) %>%
  ungroup() %>%
  mutate(prevGroup = as.numeric(as.character(prevGroup)))

md.endorse <- left_join(
  df.endorse.summary, m.pred.endorse
  ) %>% mutate(sqErr = (MAP-mean)^2)

with(md.endorse, cor(MAP, mean))

ggplot(md.endorse, aes ( x = MAP, xmin = cred_lower, xmax = cred_upper,
                 y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_point()+
  geom_errorbar(alpha = 0.3)+
  geom_errorbarh(alpha = 0.3)+
  coord_fixed()+
  xlim(0, 1)+
  ylim(0, 1)
```


Speaker optimality
```{r}
m.0 %>%
  filter(param == "speakerOptimality") %>%
  ggplot(., aes( x= val)) + 
  geom_histogram()
```

### Prevalence priors

load prevalence prior data

```{r}
df.cc.2 <- readData("pilot-ccepe-2")
```


```{r}
df.pe.2 <- df.cc.2 %>% filter(trial_type == "prevalence_prior") %>%
  mutate(verb_phrase = gsub("&quotechar","",verb_phrase),
         verb_phrase = gsub(",","",verb_phrase),
         response = as.numeric(as.character(response)))
```


##### Marginal distributions on prevalence

```{r gen-prevprior-marginals, fig.width = 8, fig.height = 5}
bind_rows(
  df.pe.2 %>% 
  rename(prevalence = response) %>%
  mutate(src = 'data') %>% 
  select(verb_phrase, src, prevalence),
  m.samp.prevalence.prior %>% 
    rename(verb_phrase = property) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(. , aes( x = prevalence, color = src))+
  geom_density(size = 1, aes( y = ..scaled.. ))+
  facet_wrap( ~ verb_phrase, nrow = 3)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```



```{r gen-prevprior-forward}
m.samp <- m.0 %>% filter(type == "prior", param != "score")

m.prior.summary <- m.samp %>%
  group_by(param, property, category) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

#Forward sample from posterior on parameters
m.samp.prior.params <- m.samp %>%
    mutate(parameter = paste(param, category, sep = "_")) %>%
    select(-param, -category, -type) %>%
    mutate(item = paste(parameter, property, sep = "_")) %>%
    group_by(item) %>%
    mutate(iteration = ave(item==item, item, FUN=cumsum)) %>%
    ungroup() %>%
    select(-item)
  
m.samp.prevalence.prior <- m.samp.prior.params %>%
    group_by(parameter, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(component1 = rbinom(1, 1, prob = mixture_NA),
       prevalence = ifelse(component1 == 1, 
                           rbeta(n = 1, 
                                 shape1 = stableFreq1_mean* stableFreq1_sampleSize,
                                 shape2 = (1-stableFreq1_mean)*stableFreq1_sampleSize),
                           rbeta(n = 1,
                                 shape1 = 1,
                                 shape2 = 100))) %>%
    ungroup() %>%
    select(property, prevalence)


# m.samp.prevalence.prior <- m.samp.prior.params %>%
#     group_by(parameter, property, iteration) %>%
#     spread(parameter, val) %>%
#     rowwise() %>%
#     mutate(component1 = rbinom(1, 1, prob = mixture_NA),
#        prevalence = ifelse(component1 == 1, 
#                            rbeta(n = 1, 
#                                  shape1 = stableFreq1_mean* stableFreq1_sampleSize,
#                                  shape2 = (1-stableFreq1_mean)*stableFreq1_sampleSize),
#                            rbeta(n = 1,
#                                  shape1 = stableFreq2_mean* stableFreq2_sampleSize,
#                                  shape2 = (1-stableFreq2_mean)*stableFreq2_sampleSize))) %>%
#     ungroup() %>%
#     select(property, prevalence)





```

##### Marginal distributions on prevalence
```{r}
bind_rows(
  df.pe.2 %>% 
  rename(prevalence = response) %>%
  mutate(src = 'data') %>% 
  select(verb_phrase, src, prevalence),
  m.samp.prevalence.prior %>% 
    rename(verb_phrase = property) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(.,
           aes( x = prevalence, color = src, lty = src))+
    #geom_density(aes(y = ..scaled..), adjust = 1.3, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~verb_phrase, nrow = 3)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
    #coord_fixed()+
    xlab("prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.title = element_blank(), legend.position = 'bottom')

```

```{r gen-prevprior, fig.width = 8, fig.height = 5}
bind_rows(
  df.pe.2 %>% 
  rename(prevalence = response) %>%
  mutate(src = 'data') %>% 
  select(verb_phrase, src, prevalence),
  m.samp.prevalence.prior %>% 
    rename(verb_phrase = property) %>%
    mutate(src = 'model') 
  ) %>%
ggplot(. , aes( x = prevalence, color = src))+
  geom_density(size = 1, aes( y = ..scaled.. ))+
  facet_wrap( ~ verb_phrase, nrow = 3)+
  scale_color_solarized()+
  scale_x_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```
- try simpler priors (e.g., 3 parameter betas, or single beta)
- more data in listener task & prior task
- make a PREVLANECE version of listener task and collect some data
skype early next week