---
title: "Pilots 3 (3/20/2017)"
output: html_notebook
---

```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(ggthemes)
library(forcats)
library(knitr)
theme_set(theme_few())

data.path <- "../data/pilots/"

readData <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-trials.csv", sep = "")))
}

readSubjectInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-subject_information.csv", sep = "")))
}
```

### Overview of Experiments:

Both experiments run 3/20/17

1. Domain restriction 2 - People NPs (n=15): Participants see conversation and are asked if the NP "people" is referring to "people who ___" or "people when ___". Aim is to see if the domain restriction is on the category or on the event (and if it varies by the type of predicate).
2. Focus - Emboldened training (n=20). Noncorpus / true experimental study. Participants are familiarized with the idea of *focus* (instantiated as bold, blue text), and are tested on it with generic statements under direct questions ("What lay eggs?" vs. "How do birds reproduce?"). The goal is to see if the bold, blue text can be used as a valid measurement for focus.


Follow-up run on 4/4/17

3. Focus - Emboldened test ( n = 9 ). Corpus version of (2).

# Domain restriction 2: People NPs (n=15)


Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-dr-people-2")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.dr <- readData("pilot-dr-people-2") %>%
  rowwise() %>%
  mutate(entire.sentence = gsub("&quotechar", "", entire.sentence),
         people_who = ifelse(response == "People who", 1, 0)) 
```


```{r}
d.dr.item.summary <- d.dr %>%
  group_by(entire.sentence) %>%
  multi_boot_standard(column = "people_who")
```

```{r fig.width = 13}
d.dr.item.summary <- d.dr.item.summary %>%
  mutate(entire.sentence = 
           factor(entire.sentence, levels = entire.sentence[order(mean)]))


ggplot(d.dr.item.summary, aes(x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Proportion 'People who' restriction")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```


## Top "people who" responses

```{r}
top.dr <- left_join(d.dr, d.dr.item.summary) %>% 
  select(entire.sentence, specific, mean, response) %>%
  filter(mean > 0.75)

top.dr[with(top.dr, order(-mean, entire.sentence, response)),] %>% kable()
```



## Top "people when" responses

```{r}
top.dr.when <- left_join(d.dr, d.dr.item.summary) %>% 
  select(entire.sentence, specific, mean, response) %>%
  filter(mean <= 0.6)

top.dr.when[with(top.dr.when, order(mean, entire.sentence, response)),] %>% kable()
```

## Intermediate responses

Will we see double domain restriction?

```{r}
intermediate.dr.when <- left_join(d.dr, d.dr.item.summary) %>% 
  select(entire.sentence, specific, mean, response) %>%
  filter(mean > 0.6, mean < 0.75)


intermediate.dr.when[with(intermediate.dr.when, order(mean, entire.sentence, response)),] %>% kable()

```




# Focus Emboldened Training (n=20)

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-emboldened-training-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.focus <- readData("pilot-emboldened-training-1")
```


Preprocess data

```{r}
d.focus <- d.focus %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         correct_response = ifelse(correct == "NP",  NP_response, 1 - NP_response),
         context = gsub("<br><b>Speaker #1</b>: ", "", context),
         context = gsub(" <br><b>Speaker #2</b>:", "", context)) %>%
  ungroup()
```

```{r}
d.focus.stat.item <- d.focus %>%
  group_by(entire.sentence, context, correct) %>%
  multi_boot_standard(column = "correct_response")
```

```{r}
ggplot(d.focus.stat.item, aes( x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper, fill = correct))+
  geom_bar(stat = 'identity', position = position_dodge(), alpha = 0.5, color = 'black')+
  geom_errorbar(position = position_dodge())+
  #theme(axis.text.x = element_text(angle = 90))+
  coord_flip()
```



# Focus Emboldened Test (n=9)

4/5/17

Flaws
- should record "correct" answer for catch trials
- should record "context" for corpus items

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-emboldened-focus-pilot-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.focus <- readData("pilot-emboldened-focus-pilot-1")
```


Catch / warm up trials

```{r}
d.focus.catch <- read.csv(paste(data.path, "pilot-emboldened-focus-1", "/", "pilot-emboldened-focus-1", "-catch_trials.csv", sep = ""))

correct.responses <- data.frame(
  entire.sentence = c("Ticks carry Lyme disease.", "Beavers build dams."),
  correct = c("VP", "NP")
)

d.focus.correct <- left_join(d.focus.catch, correct.responses) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         correct_response = ifelse(correct == "NP",  NP_response, 1 - NP_response))



d.good.workers <- d.focus.correct %>%
  select(workerid, entire.sentence, correct_response) %>%
  spread(entire.sentence, correct_response) %>%
  #group_by(workerid) %>%
  rowwise() %>%
  filter( (`Beavers build dams.` > 0.5) || (`Ticks carry Lyme disease.` > 0.5))

d.focus.correct %>%
  select(workerid, entire.sentence, correct_response) %>%
  spread(entire.sentence, correct_response) %>% kable()
```



Preprocess data

```{r}
d.focus.passed <- d.focus %>%
  filter(workerid %in% d.good.workers$workerid) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         entire.sentence = gsub("&quotechar","", entire.sentence)) %>%
  ungroup() %>%
  mutate(workerid = factor(workerid))
```

```{r fig.width = 16, fig.height = 8}
ggplot(d.focus.passed, aes( x = workerid, y = NP_response, fill = workerid))+
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  facet_wrap(~entire.sentence)+
  scale_fill_solarized()+
  geom_hline(yintercept = 0.5, lty = 3)
```


All subjects

```{r}
d.focus.all <- d.focus %>%
  mutate(pass = workerid %in% d.good.workers$workerid) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         entire.sentence = gsub("&quotechar","", entire.sentence)) %>%
  ungroup() %>%
  mutate(workerid = factor(workerid))
```

```{r fig.width = 16, fig.height = 8}
ggplot(d.focus.all, aes( x = pass, y = NP_response, fill = workerid))+
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  facet_wrap(~entire.sentence)+
  scale_fill_solarized()+
  geom_hline(yintercept = 0.5, lty = 3)
```


# Focus Emboldened Test (n=25)

4/6/17

Same as before but with 4 warm-up trials instead of 2 used in the previous verison.

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-emboldened-focus-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.focus <- readData("pilot-emboldened-focus-1")
```


Catch / warm up trials

```{r}
d.focus.catch <- read.csv(paste(data.path, "pilot-emboldened-focus-1", "/", "pilot-emboldened-focus-1", "-catch_trials.csv", sep = ""))

correct.responses <- data.frame(
  entire.sentence = c("Ticks carry Lyme disease.", "Beavers build dams."),
  correct = c("VP", "NP")
)

d.focus.correct <- left_join(d.focus.catch, correct.responses) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         correct_response = ifelse(correct == "NP",  NP_response, 1 - NP_response))



d.good.workers <- d.focus.correct %>%
  select(workerid, entire.sentence, correct_response) %>%
  spread(entire.sentence, correct_response) %>%
  #group_by(workerid) %>%
  rowwise() %>%
  filter( (`Beavers build dams.` > 0.5) || (`Ticks carry Lyme disease.` > 0.5))

d.focus.correct %>%
  select(workerid, entire.sentence, correct_response) %>%
  spread(entire.sentence, correct_response) %>% kable()
```



Preprocess data

```{r}
d.focus.passed <- d.focus %>%
  filter(workerid %in% d.good.workers$workerid) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         entire.sentence = gsub("&quotechar","", entire.sentence)) %>%
  ungroup() %>%
  mutate(workerid = factor(workerid))
```

```{r fig.width = 16, fig.height = 8}
ggplot(d.focus.passed, aes( x = workerid, y = NP_response, fill = workerid))+
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  facet_wrap(~entire.sentence)+
  scale_fill_solarized()+
  geom_hline(yintercept = 0.5, lty = 3)
```


All subjects

```{r}
d.focus.all <- d.focus %>%
  mutate(pass = workerid %in% d.good.workers$workerid) %>%
  rowwise() %>%
  mutate(NP_response = ifelse(right_side == "NP", focus, 1-focus),
         entire.sentence = gsub("&quotechar","", entire.sentence)) %>%
  ungroup() %>%
  mutate(workerid = factor(workerid))
```

```{r fig.width = 16, fig.height = 8}
ggplot(d.focus.all, aes( x = pass, y = NP_response, fill = workerid))+
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  facet_wrap(~entire.sentence)+
  scale_fill_solarized()+
  geom_hline(yintercept = 0.5, lty = 3)
```







### Mean responses 

Only passed catch trials

```{r}
d.focus.passed %>%
  group_by(entire.sentence) %>%
  multi_boot_standard(column = "NP_response") %>%
ggplot(., aes( x = entire.sentence, y = NP_response, fill = workerid))+
  geom_bar(stat = 'identity', position = position_dodge(), color = 'black')+
  facet_wrap(~)+
  scale_fill_solarized()+
  geom_hline(yintercept = 0.5, lty = 3)
```

