---
title: "Pilots 2"
output: html_notebook
---


```{r}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(ggthemes)
library(forcats)
library(knitr)
theme_set(theme_few())

data.path <- "../data/pilots/"

readData <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-trials.csv", sep = "")))
}

readSubjectInfo <- function(project){
  return(read.csv(paste(data.path, project, "/", project, "-subject_information.csv", sep = "")))
}
```

### Overview of Experiments:

All experiments run 3/6/17

1. Domain restriction - People NPs (n=18): Participants see conversation and are asked if the NP "people" is referring to "human beings", "Americans", "people in the area", or some other specific group of people. There is a practice trial where participants see an instance of "People in this area" and "People who have jobs"
2. Domain restriction - Nonpeople NPs (n=18): Participants see conversation and are asked if the NP is referring to "NPs in general" or some "specific group/type of NP". There is a practice trial where participants see an instance of "people" referring to "human beings" and referring to "people who have jobs".
3. Focus - Mixed people/non (n=18). Participants see conversation and are asked if the speaker meant NP (as opposed to other entities/things) VP, or NP VP (as opposed to doing other things / having other qualities). Participants saw a practice trial using "Birds lay eggs" under different direct questions ("What lay eggs?" vs. "How do birds reproduce?")


# Domain restriction pilot: People NPs (n=18)

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-dr-people-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.dr <- readData("pilot-dr-people-1")
```


#### Context-specific domain restriction? (i.e., "people who ___")

```{r}
dr.summary <- d.dr %>%
  mutate(response = ifelse(response == "People who", 1, 0)) %>%
   group_by(entire.sentence) %>% 
    multi_boot_standard(column = "response")
```

```{r fig.width = 13}
dr.summary %>%
  mutate(entire.sentence = factor(entire.sentence, levels = entire.sentence[order(mean)])) %>% 
  ggplot(., aes(x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Proportion Context-Specific domain restriction")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```

#### Items with greater than 0.25 "people who___" responses

```{r}
top.dr <- left_join(d.dr, dr.summary) %>% 
  select(entire.sentence, specific, mean) %>%
  filter(mean > 0.25, specific != "")

top.dr[order(-top.dr$mean),] %>% kable()
```


```{r}
dr.summary.responses <- d.dr %>%
   group_by(entire.sentence, response) %>%
   summarize(n = n())
```


### Distribution of responses

```{r fig.width = 13}
dr.summary.responses %>%
  mutate(response = factor(response, levels = c("Humans in general", "Americans", "People in the area", "People who"),
                            labels = c("Humans", "Americans", "Locals", "adhoc"))
         ) %>% 
  ggplot(., aes(x = response, y = n, fill = response))+
  geom_bar(stat = 'identity', position = position_dodge())+
  scale_fill_solarized()+
  facet_wrap(~entire.sentence) + 
  #coord_flip()+
  ylab("Proportion Specific domain restriction")+
  theme(axis.text.x = element_blank(),
        strip.text = element_text(size = 8))
```



# Domain restriction pilot: Noneople NPs (n=18)

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-dr-nonpeople-1")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.dr.nonpeople <- readData("pilot-dr-nonpeople-1")
```



```{r}
dr.nonpeople.summary <- d.dr.nonpeople %>%
   group_by(entire.sentence) %>%
  mutate(response = ifelse(response == "Specific", 1, 0)) %>%
  multi_boot_standard(column = "response")
```

```{r fig.width = 13}
dr.nonpeople.summary %>%
  mutate(entire.sentence = factor(entire.sentence, levels = entire.sentence[order(mean)])) %>% 
  ggplot(., aes(x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Proportion Specific domain restriction")+
  geom_hline(yintercept = 0.5, lty = 3)
```

```{r}
dr.table <- left_join(d.dr.nonpeople, dr.nonpeople.summary) %>% filter(response == "Specific") %>%
  select(entire.sentence, specific, mean) %>%
  filter(mean > 0.25, specific != "")

dr.table[order(-dr.table$mean),] %>% kable()

```

# Focus pilot (n=18)

Did people enjoy the experiment?

```{r}
df.info <- readSubjectInfo("pilot-focus-2")
table(df.info$enjoyment)
```
Comments?

```{r}
df.info %>% select(comments) %>% filter(comments != "") %>% kable()
```


```{r}
d.focus <- readData("pilot-focus-2")
```

```{r fig.width = 13}
d.focus.summary <- d.focus %>%
  group_by(entire.sentence, noun.phrase) %>%
  mutate(response = ifelse(focus == "NP", 1, 0)) %>%
  multi_boot_standard(column = "response") %>%
  ungroup() %>%
  mutate(entire.sentence = factor(entire.sentence, levels = entire.sentence[order(mean)]))


d.focus.summary %>%
  ggplot(., aes(x = entire.sentence, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge())+
  geom_errorbar(position = position_dodge())+
  coord_flip()+
  ylab("Proportion NP focus")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```

```{r eval = F}
d.focus.summary %>%
  group_by(noun.phrase) %>%
  summarize(n = n()) %>%
  kable()
```

People vs. non-people?

```{r fig.width = 4}
d.focus %>%
  mutate(people = ifelse(noun.phrase == "people", "people", "nonpeople")) %>%
  group_by(people) %>%
  mutate(response = ifelse(focus == "NP", 1, 0)) %>%
  multi_boot_standard(column = "response") %>%
  ggplot(., aes(x = people, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_bar(stat = 'identity', position = position_dodge(0.9), width = 0.9)+
  geom_errorbar(position = position_dodge(0.9), width = 0.3)+
  ylab("Proportion NP focus")+
  ylim(0,1)+
  geom_hline(yintercept = 0.5, lty = 3)
```

